TRITON: Texture Recovering Image Translation Network [[TODO Make catchier]]

### 2022-05-16 paper.tex
Added new abstract

\begin{abstract}
	Unpaired image translation algorithms can be used for sim-to-real tasks, but they often fail to generate temporally consistent results.
	Because of this, the details or even identity of a particular object might change as it moves across a scene.
	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
	Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly [[ie. no need for optical flow]].
	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
\end{abstract}

>>>>

\begin{abstract}
	Unpaired image translation algorithms can be used for sim-to-real tasks, but they often fail to generate temporally consistent results.
	Because of this, the details or even identity of a particular object might change as it moves across a scene.
	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm. [[Too many adjectives?]]
	Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
	By settling on particular albedos for scene objects, we ensure consistency between frames statelessly. [[ie. no need for optical flow]]
	In addition, we introduce a translation consistency loss that further improves the consistency of the results. [[I called this “view consistency loss” in the code and to you, but translation consistency loss might be a better name? What do you think?]]
	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
\end{abstract}
